---
title: "Scraping Examples"
author: "Kaitlyn Westra"
date: "11/16/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

# Solar Flares

```{r}
if (!file.exists('flare.data2')) {
  #download.file("https://archive.ics.uci.")
  #get file from UCI ML archive
}
```

```{r}
#way more stuff here
```




# Wunderground

```{r}
library(rvest)
```

```{r}
html <- read_html('https://www.wunderground.com/history/monthly/KGRR/date/2020-11')
html %>%
  html_nodes("lib-city-history-observation table")
```

Look at inspect = = > inspector and = = > network.
Get the json object.
Copy --> copy response.
Make new text file & paste that!

I obviously did something wrong, as my .json isn't telling me all the information I want. I think I copied the wrong .json file, but I don't know where the right one is. But... this is what it would look like if I had used the right file.

```{r}
library(jsonlite)
weather_hist <- jsonlite::read_json("./data/wunderground-hist.json", simplifyVector = TRUE)
observations <- weather_hist$observations
glimpse(observations)
weather_hist$status %>% glimpse()
```

when you're typing, look at the grey thing for a function to see which package you're using it from  
turns anything ambiguous into an error


BigQuery: Google Cloud Platform (CalvinDSDev)  
Free to access from Google.

