---
title: "Scraping Examples"
author: "K Arnold"
date: "11/16/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(conflicted)
library(tidyverse)
library(rvest)
```

## Solar Flare Data

```{r}
if (!file.exists("flare.data2")) {
  download.file("https://archive.ics.uci.edu/ml/machine-learning-databases/solar-flare/flare.data2", "flare.data2")
}
```

```{r}
read_delim("flare.data2", delim = " ", skip = 1)#, col_names = FALSE)
```

## Wunderground

<https://www.wunderground.com/history/monthly/KGRR/date/2020-11>

```{r}
library(rvest)
```

```{r}
html <- read_html('https://www.wunderground.com/history/monthly/KGRR/date/2020-11')
```

```{r}
html %>% html_nodes("lib-city-history-observation table")
```

```{r}
library(jsonlite)
weather_hist <- jsonlite::read_json("wunderground-hist.json", simplifyVector = TRUE)
observations <- weather_hist$observations
```

```{r}
glimpse(observations)
```

## NOAA weather data

You can request Local Climatological Data from <https://www.ncdc.noaa.gov/data-access/land-based-station-data/land-based-datasets>.

With a bit more sleuthing to discover the station ID, you can download the
historical data directly from, e.g., <https://www.ncei.noaa.gov/data/global-hourly/access/2020/72635094860.csv>
(Grand Rapids).

The CSVs have some weird formatting, beware.

## BigQuery

[Reddit comments](https://www.reddit.com/r/bigquery/comments/3cej2b/17_billion_reddit_comments_loaded_on_bigquery/)

The example COVID query we ran:

```
WITH
  country_pop AS (
  SELECT
    country_code AS iso_3166_1_alpha_3,
    year_2018 AS population_2018
  FROM
    `bigquery-public-data.world_bank_global_population.population_by_country`)
SELECT
  country_code,
  country_name,
  cumulative_confirmed AS confirmed_cases,
  population_2018,
  ROUND(cumulative_confirmed/population_2018 * 100,2) AS case_percent
FROM
  `bigquery-public-data.covid19_open_data.covid19_open_data`
JOIN
  country_pop
USING
  (iso_3166_1_alpha_3)
WHERE
  date = '2020-11-13'
  AND aggregation_level = 0
  AND population_2018 > 100000000
ORDER BY
  case_percent DESC
```

(which was based on one of the examples on Google's [COVID-19 Public Datasets](https://console.cloud.google.com/marketplace/product/bigquery-public-datasets/covid19-public-data-program) page)
